### 2025-02-19 paper/sections/other/constraints.qmd
convergence

function plot_db(model, ces; _xlab="Debt", _ylab="Age")

@@

    # Objective:
    generator = GenericGenerator()
    opt_state = Flux.setup(Descent(), model)
    conv = MaxIterConvergence(25)

>>>>

function plot_db(model, ces; _xlab="Debt", _ylab="Age", plot_contour::Bool=false)

@@

    # Objective:
    generator = GenericGenerator()
    opt_state = Flux.setup(Descent(), model)
    conv = DecisionThresholdConvergence(decision_threshold=0.99)
